Factors affecting reliablity of state-space age-structured assessment models

### 2023-09-15 Project_0/paper/paper.Rmd

---
title: Factors affecting reliablity of state-space age-structured assessment models
author: 
  - Timothy J. Miller^1^
  - A. Applegate 
  - G. Britten
  - E. N. Brooks
  - G. Fay
  - A. Hansell
  - C. M. Legault
  - B. Muffley
  - J. Wiedenmann
date: ''
fontsize: 12pt
output:
  pdf_document:
    citation_package: natbib
    fig_caption: yes
    includes:
      in_header:
      - options.sty
      - journalshortcuts.tex
    keep_tex: yes
    number_sections: yes
  html_document:
    df_print: paged
  word_document: default
header-includes:
- \usepackage{xspace}
- \usepackage{bm}
- \usepackage{caption,graphics}
- \usepackage{graphicx}
- \usepackage{makecell}
- \renewcommand\figurename{Fig.}
- \captionsetup{labelsep=period, singlelinecheck=false}
- \newcommand{\changesize}[1]{\fontsize{#1pt}{#1pt}\selectfont}
- \renewcommand{\arraystretch}{1.5}
- \renewcommand\theadfont{}
csl: canadian-journal-of-fisheries-and-aquatic-sciences.csl
biblio-style: cjfas2.bst
---

@@

SR estimation or not

Initial values for BH parameters are the true values.
Initial values for mean R model = true R0.

M estimation or not

NAA_re
Random effects on Recruitment only or random effects on recruitment and transitions among older numbers at age.

M_re
Random effects on Recruitment only, M constant across age .

sel_re
Random effects on Recruitment only, fleet logistic selectivity RE model?

q_re
Random effects on Recruitment only, one survey catchability RE model?

@@

\begin{landscape}
\begin{figure}
\caption{Median relative bias of for SSB for estimating models fitted to data sets simulated with R+q process errors.  Estimation models do not assume a stock-recruit function and M is fixed at the true value.}\label{q_om_em_R_MF_relbias_ssb}
\begin{center}
\includegraphics[width = \textwidth]{q_om_R_MF_relbias_ssb.png}
\end{center}
\end{figure}
\end{landscape}

\begin{landscape}
\begin{figure}
\caption{Median relative bias of for SSB for estimating models fitted to data sets simulated with R+q process errors. Estimation models do not assume a stock-recruit relationship and estimate M.}\label{q_om_em_R_ME_relbias_ssb}
\begin{center}
\includegraphics[width = \textwidth]{q_om_R_ME_relbias_ssb.png}
\end{center}
\end{figure}
\end{landscape}

\begin{landscape}
\begin{figure}
\caption{Median relative bias of for SSB for estimating models fitted to data sets simulated with R+q process errors. Estimation models assume a BH stock-recruitment function and M is fixed at the true value.}\label{q_om_em_BH_MF_relbias_ssb}
\begin{center}
\includegraphics[width = \textwidth]{q_om_BH_MF_relbias_ssb.png}
\end{center}
\end{figure}
\end{landscape}

\begin{landscape}
\begin{figure}
\caption{Median relative bias of for SSB for estimating models fitted to data sets simulated with R+q process errors. Estimation models assume a BH stock-recruitment function and estimate M.}\label{q_om_em_BH_ME_relbias_ssb}
\begin{center}
\includegraphics[width = \textwidth]{q_om_BH_ME_relbias_ssb.png}
\end{center}
\end{figure}
\end{landscape}

>>>>

---
title: Factors affecting reliablity of state-space age-structured assessment models
author: 
  - Timothy J. Miller^1^
  - Andrew Applegate 
  - Greg Britten
  - Elizabeth N. Brooks
  - Gavin Fay
  - Alex Hansell
  - Christopher M. Legault
  - Brandon Muffley
  - Brian C. Stock
  - John Wiedenmann
date: ''
fontsize: 12pt
output:
  pdf_document:
    citation_package: natbib
    fig_caption: yes
    includes:
      in_header:
      - options.sty
      - journalshortcuts.tex
    keep_tex: yes
    number_sections: yes
  html_document:
    df_print: paged
  word_document: default
header-includes:
- \usepackage{xspace}
- \usepackage{bm}
- \usepackage{caption,graphics}
- \usepackage{graphicx}
- \usepackage{makecell}
- \renewcommand\figurename{Fig.}
- \captionsetup{labelsep=period, singlelinecheck=false}
- \newcommand{\changesize}[1]{\fontsize{#1pt}{#1pt}\selectfont}
- \renewcommand{\arraystretch}{1.5}
- \renewcommand\theadfont{}
csl: canadian-journal-of-fisheries-and-aquatic-sciences.csl
biblio-style: cjfas2.bst
---

@@

The observation error variance of the environmental observations and aggregate catch and indices were all assumed known at the true values.

@@

\begin{landscape}
\begin{figure}
\caption{Median relative bias of SSB for estimating models fitted to data sets simulated with R+q process errors.  Estimation models do not assume a stock-recruit function and M is fixed at the true value.}\label{q_om_em_R_MF_relbias_ssb}
\begin{center}
\includegraphics[width = \textwidth]{q_om_R_MF_relbias_ssb.png}
\end{center}
\end{figure}
\end{landscape}

\begin{landscape}
\begin{figure}
\caption{Median relative bias of SSB for estimating models fitted to data sets simulated with R+q process errors. Estimation models do not assume a stock-recruit relationship and estimate M.}\label{q_om_em_R_ME_relbias_ssb}
\begin{center}
\includegraphics[width = \textwidth]{q_om_R_ME_relbias_ssb.png}
\end{center}
\end{figure}
\end{landscape}

\begin{landscape}
\begin{figure}
\caption{Median relative bias of SSB for estimating models fitted to data sets simulated with R+q process errors. Estimation models assume a BH stock-recruitment function and M is fixed at the true value.}\label{q_om_em_BH_MF_relbias_ssb}
\begin{center}
\includegraphics[width = \textwidth]{q_om_BH_MF_relbias_ssb.png}
\end{center}
\end{figure}
\end{landscape}

\begin{landscape}
\begin{figure}
\caption{Median relative bias of SSB for estimating models fitted to data sets simulated with R+q process errors. Estimation models assume a BH stock-recruitment function and estimate M.}\label{q_om_em_BH_ME_relbias_ssb}
\begin{center}
\includegraphics[width = \textwidth]{q_om_BH_ME_relbias_ssb.png}
\end{center}
\end{figure}
\end{landscape}

### Beverton-Holt parameter estimation

\begin{landscape}
\begin{figure}
\caption{Median relative error of Beverton-Holt stock recruit parameters for estimating models with correct process error assumptions fitted to data sets simulated with R and R+S process errors. Estimation models either assume the correct natural mortality rate or estimate it.}\label{naa_om_SR_relbias}
\begin{center}
\includegraphics[width = \textwidth]{naa_om_SR_relerror.png}
\end{center}
\end{figure}
\end{landscape}

\begin{landscape}
\begin{figure}
\caption{Median relative error of Beverton-Holt stock recruit parameters for estimating models with correct process error assumptions fitted to data sets simulated with R+M process errors. Estimation models either assume the correct natural mortality rate or estimate it.}\label{M_om_SR_relbias}
\begin{center}
\includegraphics[width = \textwidth]{M_om_SR_relerror.png}
\end{center}
\end{figure}
\end{landscape}

\begin{landscape}
\begin{figure}
\caption{Median relative error of Beverton-Holt stock recruit parameters for estimating models with correct process error assumptions fitted to data sets simulated with R+Sel process errors. Estimation models either assume the correct natural mortality rate or estimate it.}\label{Sel_om_SR_relbias}
\begin{center}
\includegraphics[width = \textwidth]{Sel_om_SR_relerror.png}
\end{center}
\end{figure}
\end{landscape}

\begin{landscape}
\begin{figure}
\caption{Median relative error of Beverton-Holt stock recruit parameters for estimating models with correct process error assumptions fitted to data sets simulated with R+q process errors. Estimation models either assume the correct natural mortality rate or estimate it.}\label{q_om_SR_relbias}
\begin{center}
\includegraphics[width = \textwidth]{q_om_SR_relerror.png}
\end{center}
\end{figure}
\end{landscape}

### (Mean) natural mortality rate estimation

\begin{landscape}
\begin{figure}
\caption{Median relative error of (mean) natural mortality rate for estimating models with correct process error assumptions fitted to data sets simulated with R and R+S process errors. Estimation models assumed either no stock-recruit relationship or estimated a Beverton-Holt relationship.}\label{naa_om_M_relbias}
\begin{center}
\includegraphics[width = \textwidth]{naa_om_M_relerror.png}
\end{center}
\end{figure}
\end{landscape}

\begin{landscape}
\begin{figure}
\caption{Median relative error of (mean) natural mortality rate for estimating models with correct process error assumptions fitted to data sets simulated with R+M process errors. Estimation models assumed either no stock-recruit relationship or estimated a Beverton-Holt relationship.}\label{M_om_M_relbias}
\begin{center}
\includegraphics[width = \textwidth]{M_om_M_relerror.png}
\end{center}
\end{figure}
\end{landscape}

\begin{landscape}
\begin{figure}
\caption{Median relative error of (mean) natural mortality rate for estimating models with correct process error assumptions fitted to data sets simulated with R+Sel process errors. Estimation models assumed either no stock-recruit relationship or estimated a Beverton-Holt relationship.}\label{Sel_om_M_relbias}
\begin{center}
\includegraphics[width = \textwidth]{Sel_om_M_relerror.png}
\end{center}
\end{figure}
\end{landscape}

\begin{landscape}
\begin{figure}
\caption{Median relative error of (mean) natural mortality rate for estimating models with correct process error assumptions fitted to data sets simulated with R+q process errors. Estimation models assumed either no stock-recruit relationship or estimated a Beverton-Holt relationship.}\label{q_om_M_relbias}
\begin{center}
\includegraphics[width = \textwidth]{q_om_M_relerror.png}
\end{center}
\end{figure}
\end{landscape}
